Plots for Latent Hawkes Paper

### 2020-07-30 output_scripts/Paper_Plots.Rmd
rewrite the simulated stan fits to enfore the stationarity condition

@@

```{r fig-slides-predict}
load("../output/plot_N_predict_new.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm),
            se = sd/sqrt(n))

@@

temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
p4_slides <- temp_plot_df %>% #filter(method != "C-HP") %>% 
  #filter(method != "I-MMHP") %>%
  ggplot(aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) + 
  #ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) #+ ylim(c(0,1000))
p4_slides

>>>>

```{r fig-pred-cohort-slides, include=slides_plots,eval=slides_plots, fig.height=3}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest
# 3 looks nice

temp_plot_df <- predict_day_norm_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
#png(paste(plot_path,"real_predict_N_one_cohort.png",sep=""),width=600,height=300)
p3_slides <- temp_plot_df %>%
  filter(method != "I-MMHP") %>%
  rowwise() %>%
  #mutate(norm = min(norm,100)) %>%
  ggplot( aes(x = method, y = norm, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(),
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") +
  ylim(0, 80) +
  NULL
p3_slides
```

@@

```{r fig-slides-predict,include=slides_plots,eval=slides_plots,fig.height=3}
load("../output/plot_N_predict.RData")
temp_plot_df <- all_cohort_norm_df %>% 
  group_by(day, method) %>% 
  summarise(avg=mean(norm), n= n(), sd=sd(norm),
            se = sd/sqrt(n))

@@

temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
p4_slides <- temp_plot_df %>% #filter(method != "C-HP") %>% 
  filter(method != "I-MMHP") %>%
  ggplot(aes(x=day, y=avg, group=method, color=method)) + 
  geom_line(size=1.2, alpha=0.8, position=position_dodge(0.2)) +
  geom_errorbar(aes(ymin=avg-sd, ymax=avg+sd), width=0.8, size=0.8, alpha=0.8,
                 position=position_dodge(0.2)) +
  scale_color_manual(values = viridis::viridis(5)) + 
  #ggtitle("(b)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_text(size = 18)) +
  xlab("Prediction horizon (day)") + 
  ylab("Frobenius norm of error") + 
  coord_cartesian(ylim=c(2.5,57.5)) + 
  guides(color=guide_legend(title="Model")) #+ ylim(c(0,1000))
p4_slides
